\documentclass[11pt]{moderncv}
\moderncvstyle[roman]{casual}
\phone{+86-186-0865-1884} \email{JY369356904@163.com}
\address{Northeastern University, Shenyang, China}{}
\def\ConTeXt{%
  C%
  \kern-.0333emo%
  \kern-.0333emn%
  \kern-.0667em\TeX%
  \kern-.0333emt}

\newcommand{\listitem}[1]{\textbullet\hspace{1em}\parbox[t]{13cm}{#1}\vspace{0.5em}}

\definecolor{see}{rgb}{0.5,0.5,0.5}
\newcommand{\up}[1]{\ensuremath{^\textsf{\scriptsize#1}}}
\newcounter{count}

\begin{document}

\begin{CJK*}{GBK}{kai}
 %\firstname{Yi} \familyname{Jiang}
 \cnname{\hspace{0.2em}\color{blue}{Yi Jiang}}
 \maketitle
%\makequote
\vspace{-12mm}
%\rule{17cm}{0.4mm}
%\section{Contact Information}

\parbox[t]{1.7cm}{
                \textbf{Address}\\
                \textbf{}}
\parbox[t]{7cm}{State Key Lab of Synthetic Automation \\
                of Process Industries\\
                International Joint Research Laboratory \\
                of Integrated Automation\\
                Northeastern University Mail Box 309\\
                3-11 Wenhua Road, Heping District\\
                Shenyang Liaoning 110819, China}
\parbox[t]{2cm}{
               \textbf{Position}\\
               \textbf{E-mail}\\
               \textbf{Phone}\\
               \\
               \textbf{Homepage}
               }
\hspace{.3em}
\parbox[t]{5cm}{
               Ph.D. student\\
               JY369356904@163.com\\
               Yijiang.Ezhou@gmail.com\\
               +86-186-0865-1884\\
               yijiang1992.github.io
               }
\vspace{3mm}

\section{Experiences}

\cventry{2018/3-2019/3}{University of Alberta (UA)}{}{Edmonton, Alberta, Canada}{}{}
\cvline{$\bullet$}{\textbf{Research Assistant}}
\cvline{$\bullet$}{\textbf{Advisor:} \textbf{Prof. Tongwen Chen} (IEEE Fellow, IFAC Fellow, member of the Canadian Academy of Engineering)}
\cvline{$\bullet$}{\textbf{Research Lab:} Department of Electrical and Computer Engineering}
%
\cventry{2017/1-2017/7}{University of Texas at Arlington (UTA)}{}{Arlington, TX, USA}{}{}
\cvline{$\bullet$}{\textbf{Visiting Scholar}}
\cvline{$\bullet$}{\textbf{Advisor:} \textbf{Prof. Frank L. Lewis} (IEEE Fellow, IFAC Fellow, member of the National Academy of Inventors)}
\cvline{$\bullet$}{\textbf{Research Lab:} University of Texas at Arlington Research Institute}

\section{Education}
%
\cventry{2014/9-2020/4}{Northeastern University}{}{NEU, a ``Project 985'', ``Project 211'' university, Shenyang, China}{}{}
\cvline{$\bullet$}{\textbf{M.Eng. and phD in Control Theory and Engineering}, Entrance examination waived}\vspace{0.5mm}
\cvline{$\bullet$}{\textbf{Advisor:} \textbf{Prof. Tianyou Chai} (IEEE Fellow, IFAC Fellow, member of the Chinese Academy of Engineering, an Academician of International Eurasian Academy of Sciences, Distinguished Visiting Fellow of the Royal Academy of Engineering, Invitation Fellow of Japan Society for the Promotion of Science)}
\cvline{$\bullet$}{\textbf{Research Lab:} State Key Lab of Synthetic Automation of Process Industries}
%
\cventry{2010/9-2014/6}{Northeastern University}{}{NEU, a ``Project 985'', ``Project 211'' university, Shenyang, China}{}{}
\cvline{$\bullet$}{\textbf{B.Eng. in Automation}, College of Information Science and Engineering}

\section{Research Experiences}
%
\cventry{2018/3-present}{Event-driven control system}{}{Department of Electrical and Computer Engineering}{University of Alberta} {}
\cvline{$\bullet$}{\textbf{Advisor:} \textbf{Tongwen Chen} (IEEE Fellow, IFAC Fellow, member of the Canadian Academy of Engineering)}
\cvline{$\bullet$}{\textbf{Research Direction:} Algorithm research}
%
\cventry{2017/1-present}{Industrial process operational optimal control based on reinforcement learning}{}{University of Texas at Arlington Research Institute}{University of Texas at Arlington} {}
\cvline{$\bullet$}{\textbf{Advisor:} \textbf{Prof. Frank L. Lewis} (IEEE Fellow, IFAC Fellow, member of the National Academy of Inventors)}%\hspace{.1em}
\cvline{$\bullet$}{\textbf{Research Direction:} Algorithm research}
%
\cventry{2013/6-present}{Industrial process operational optimal control in double network environments}{}{State Key Lab of Synthetic Automation of Process Industries}{Northeastern University} {}
\cvline{$\bullet$}{\textbf{Advisor:} \textbf{Prof. Tianyou Chai} (IEEE Fellow, IFAC Fellow, member of the Chinese Academy of Engineering, an Academician of International Eurasian Academy of Sciences, Distinguished Visiting Fellow of the Royal Academy of Engineering, Invitation Fellow of Japan Society for the Promotion of Science)}
\cvline{$\bullet$}{\textbf{Research Direction:} Network operational control, development of wireless control system}
%
\cventry{2013/8-2013/12}{Research on target tracking detection based on the quadrotor and visual}{}{Artificial Intelligence and Robot Institute of Information Science and Engineering College}{Northeastern University} {}
\cvline{$\bullet$}{\textbf{Advisor:}  \textbf{Prof. Yunzhou Zhang}}
\cvline{$\bullet$}{\textbf{Research Direction:} Quadrotor visual image processing, control algorithm}
%
\cventry{2012/10-2013/8}{Freescale smart car based on the visual}{}{Freescale Smart Car Lab}{Northeastern University} {}
\cvline{$\bullet$}{\textbf{Advisor:} \textbf{Prof. Shuping Chen, Lector Shiguang Wen}}
\cvline{$\bullet$}{\textbf{Research Direction:} Hardware system of smart car, route identification, tracking and control algorithm}
%
\cventry{2011/10-2013/5}{The criminal search system based on the visual}{}{Automatic Institute of Information Science and Engineering College}{Northeastern University} {}
\cvline{$\bullet$}{\textbf{Advisor:} \textbf{Prof. Mingxin Jia}}
\cvline{$\bullet$}{\textbf{Research Direction:} Face detection and recognition}
%
\cventry{2011/10-2012/10}{``NiuNiu'' Robot football contest}{}{Artificial Intelligence and Robot Institute of Information Science and Engineering College}{Northeastern University} {}
\cvline{$\bullet$}{\textbf{Advisor:}  \textbf{Prof. Guofeng Tong}}
\cvline{$\bullet$}{\textbf{Research Direction:} Robot visual image processing}

\section{Project}

\cventry{2018.01-2019.12}{Flotation process operational control method}{Northeastern University doctoral research and innovation project}{Funds: 40 thousand}{Presiding officer}{}{}
\cventry{2016.01-2020.12}{Architecture, design method and application verification of industrial cognitive network oriented to intelligent enterprises}{Key Project of Natural Science Foundation of China(No. 61533015)}{Funds: 3.8 million}{Participant}{}{}
\cventry{2014.01-2018.12}{Industrial production process control and optimization control methods of dual-network environment}{Key Project of Natural Science Foundation of China(No. 61333012)}{Funds: 3 million}{Participant}{}{}
\cventry{2014.01-2016.12}{Research on feedback control method of industrial process operation based on Wireless Sensor Network}{Youth Science Foundation of Project Natural Science Foundation of China project(No.61304028)}{Funds: 0.25 million}{Participant}{}{}

\section{Journal Paper}\setcounter{count}{1}

\cvline{[\thecount]}{\textbf{Yi Jiang}, Jialu Fan$^*$, Weinan Gao, Tianyou Chai, Frank L. Lewis. Cooperative Adaptive Optimal Output Regulation of Discrete-Time Nonlinear Multi-Agent Systems. \textbf{Automatica}, to be published.}\addtocounter{count}{1}
\cvline{[\thecount]}{\textbf{Yi Jiang}, Dawei Shi, Jialu Fan$^*$, Tianyou Chai, Tongwen Chen. Set-Valued Feedback Control and its Application to Event-Triggered Sampled-Data Systems. \textbf{IEEE Transactions on Automatic Control}, to be published.}\addtocounter{count}{1}
\cvline{[\thecount]}{Wenyan Pang, Jialu Fan$^*$, \textbf{Yi Jiang}, Frank L. Lewis. Optimal Output Regulation of Partially Linear Discrete-Time Systems Using Reinforcement Learning. Acta Automatica Sinica, to be published.}\addtocounter{count}{1}
\cvline{[\thecount]}{Jialu Fan, Qian Wu, \textbf{Yi Jiang}$^*$, Tianyou Chai, Frank L. Lewis. Model-Free Optimal Output Regulation for Linear Discrete-Time Lossy Networked Control Systems. IEEE Transactions on Systems, Man, and Cybernetics: Systems, to be published, doi: 10.1109/TSMC.2019.2946382.}\addtocounter{count}{1}
\cvline{[\thecount]}{Zhen Li, Jialu Fan*, \textbf{Yi Jiang}, Tianyou Chai. A model-Free $H_\infty$ Method Based on Off-policy with Output Data Feedback. Acta Automatica Sinica, to be published.}\addtocounter{count}{1}
\cvline{[\thecount]}{\textbf{Yi Jiang}, Bahare Kiumarsi, Jialu Fan$^*$, Tianyou Chai, Jinna Li, Frank L. Lewis. Optimal Output Regulation of Linear Discrete-time Systems with Unknown Dynamics using Reinforcement Learning. \textbf{IEEE Transactions on Cybernetics}, to be published, doi: 10.1109/TCYB.2018.2890046.}\addtocounter{count}{1}
\cvline{[\thecount]}{Wenqian Xue, Jialu Fan$^*$, Victor Gabriel Lopez Mejia, Jinna Li$^*$, \textbf{Yi Jiang}, Tianyou Chai, Frank L. Lewis. New Methods for Optimal Operational Control of Industrial Processes using Reinforcement Learning on Two Time-Scales. \textbf{IEEE Transactions on Industrial Informatics}, 2020, 16(5): 3085-3099, doi: 10.1109/TII.2019.2912018.}\addtocounter{count}{1}
\cvline{[\thecount]}{Qian Wu, Jialu Fan$^*$, \textbf{Yi Jiang}, Tianyou Chai. Data-Driven Dual-rate Control for Mixed Separation Thickening Process in a Wireless Network Environment. \textbf{Acta Automatica Sinica}, 2019, 45(6): 1128-1141, doi: 10.16383/j.aas.c180202.}\addtocounter{count}{1}
\cvline{[\thecount]}{\textbf{Yi Jiang}, Jialu Fan$^*$, Tianyou Chai, Frank L. Lewis. Dual-Rate Operational Optimal Control for Flotation Industrial Process with Unknown Operational Model. \textbf{IEEE Transactions on Industrial Electronics}, 2019, 66(6): 4587-4599, doi: 10.1109/TIE.2018.2856198.}\addtocounter{count}{1}
\cvline{[\thecount]}{Jinna Li, Tianyou Chai$^*$, Frank L. Lewis, Zhengtao Ding, \textbf{Yi Jiang}. Off-Policy Interleaved $Q$-Learning: Optimal Control for Affine Nonlinear Discrete-Time Systems. \textbf{IEEE Transactions on Neural Networks and Learning Systems}, 2019, 30(5): 1308-1320, doi: 10.1109/TNNLS.2018.2861945.}\addtocounter{count}{1}
\cvline{[\thecount]}{\textbf{Yi Jiang}, Jialu Fan$^*$, Yao Jia, Tianyou Chai. Data-Driven Flotation Process Operational Feedback Decoupling Control. \textbf{Acta Automatica Sinica}, 2019, 45(4): 759-770, doi: 10.16383/j.aas.2018.c170552.}\addtocounter{count}{1}
\cvline{[\thecount]}{Xinglong Lu, Bahare Kiumarsi, Tianyou Chai$^*$, \textbf{Yi Jiang}, Frank L. Lewis. Operational Control of Mineral Grinding Processes Using Adaptive Dynamic Programming and Reference Governor. \textbf{IEEE Transactions on Industrial Informatics}, 2019, 15(4): 2210-2221, doi: 10.1109/TII.2018.2868473.}\addtocounter{count}{1}
\cvline{[\thecount]}{\textbf{Yi Jiang}, Jialu Fan$^*$, Tianyou Chai, Frank L. Lewis, Jinna Li. Tracking Control for Linear Discrete-time Networked Control Systems with Unknown Dynamics and Dropout. \textbf{IEEE Transactions on Neural Networks and Learning Systems},  2018, 29(10): 4607-4620, doi: 10.1109/TNNLS.2017.2771459.}\addtocounter{count}{1}
\cvline{[\thecount]}{\textbf{Yi Jiang}, Tannong Li, Jialu Fan$^*$. Model Predictive Control-based Setpoint Regulation in Industrial Processes. \textbf{Control Engineering of China}, 2018, 25(6): 980-984, doi: 10.14107/j.cnki.kzgc.150360.}\addtocounter{count}{1}
\cvline{[\thecount]}{\textbf{Yi Jiang}, Jialu Fan$^*$, Tianyou Chai, Jinna Li, Frank L. Lewis. Data-Driven Flotation Industrial Process Operational Optimal Control Based on Reinforcement Learning. \textbf{IEEE Transactions on Industrial Informatics}, 2018, 14(5): 1974-1989, doi: 10.1109/TII.2017.2761852. }\addtocounter{count}{1}
\cvline{[\thecount]}{Jialu Fan$^*$, \textbf{Yi Jiang}, Tianyou Chai. MPC-Based Setpoint Compensation with Unreliable Wireless Communications and Constrained Operational Conditions. \textbf{Neucomputing}, 2017, 270: 110-121, doi: 10.1016/j.neucom.2016.10.098.}\addtocounter{count}{1}
\cvline{[\thecount]}{Jialu Fan$^*$, \textbf{Yi Jiang}, Tianyou Chai. Operational Feedback Control of Industrial Processes in a Wireless Network Environment. \textbf{Acta Automatica Sinica}, 2016, 42(8): 1166-1174, doi: 10.16383/j.aas.2016.c150771.}\addtocounter{count}{1}
\cvline{[\thecount]}{Yannong Li; Tinglan Li; \textbf{Yi Jiang}; Jialu Fan$^*$. Adaptive PID Control of Quadrotor Based on RBF Neural Network. \textbf{Control Engineering of China}, 2016, 23(3): 378-382, doi: 10.14107/j.cnki.kzgc.150303.}\addtocounter{count}{1}

\section{Conference Paper}\setcounter{count}{1}
\cvline{[\thecount]}{Jialu Fan$^*$, Wenkuan Feng, \textbf{Yi Jiang}. Operational Feedback Control of Industrial Process Under Wireless Packet Disordering. 2019 International Conference on Advanced Mechatronic Systems (ICAMechS). 2019: 87-91, doi: 10.1109/ICAMechS.2019.8861672. }\addtocounter{count}{1}
\cvline{[\thecount]}{Jialu Fan$^*$, Zhen Li, \textbf{Yi Jiang}, Tianyou Chai, Frank L. Lewis. Model-Free Linear Discrete-Time System $H_\infty$ Control Using Input-Output Data. 2018 International Conference on Advanced Mechatronic Systems (ICAMechS). 2018: 207-212, doi: 10.1109/ICAMechS.2018.8506843. }\addtocounter{count}{1}
\cvline{[\thecount]}{Qian Wu, Jialu Fan$^*$, \textbf{Yi Jiang}. Dual-rate Operational Optiaml Control for Linear Flotation Process. Information and Automation, 2017 IEEE International Conference on. IEEE, 2017: 448-453, doi: 10.1109/ICInfA.2017.8078950.}\addtocounter{count}{1}
\cvline{[\thecount]}{Wenqian Xue, Jialu Fan$^*$, \textbf{Yi Jiang}. Flotation Process with Model Free Adaptive Control. Information and Automation, 2017 IEEE International Conference on. IEEE, 2017: 442-447, doi: 10.1109/ICInfA.2017.8078949.}\addtocounter{count}{1}
\cvline{[\thecount]}{Yannong Li, \textbf{Yi Jiang}, Yutao Fu, Jialu Fan$^*$. Prediction-Prevention Mathematic Model of Ebola's Spread and Eradication. \textbf{Proceeding of the 2015 IEEE International Conference on Information and Automation (ICIA)}, 2015: 1774-1779, doi: 10.1109/ICInfA.2015.7279574. }\addtocounter{count}{1}
\cvline{[\thecount]}{\textbf{Yi Jiang}, Jialu Fan$^*$, Tianyou Chai, Tongwen Chen. Setpoint Dynamic Compensation via Output Feedback Control with Network Induced Time Delays. Proceeding of the American Control Conference, Chicago, 2015: 5384-5389, doi: 10.1109/ACC.2015.7172181. }\addtocounter{count}{1}
\cvline{[\thecount]}{\textbf{Yi Jiang}; Jialu Fan$^*$; Yewei Zhang; Lei Wang. An Experimental Study on Integrated Network-based Operational Control Method. Mechatronics and Control (ICMC), 2014 1st International Conference on. IEEE, 2014: 1995-2000, doi: 10.1109/ICMC.2014.7231913. }\addtocounter{count}{1}
\cvline{[\thecount]}{Yewei Zhang, Jialu Fan$^*$, \textbf{Yi Jiang}, Lei Wang. Semi-physical Simulation Platform for Double Layer Network-Based Operational Control. Intelligent Control and Automation (WCICA), 2014 11th World Congress on. IEEE, 2014: 1118-1123, doi: 10.1109/WCICA.2014.7052875. }\addtocounter{count}{1}
\cvline{[\thecount]}{Mingxing Jia$^*$, Junqiang Du, Tao Cheng, Ning Yang, \textbf{Yi Jiang}, Zhen Zhang. An Improved Detection Algorithm of Face with Combining Adaboost and SVM. Control and Decision Conference (CCDC), 2013 25th Chinese. IEEE, 2013: 2459-2463, doi: 10.1109/CCDC.2013.6561352. }\addtocounter{count}{1}

\section{Patent}\setcounter{count}{1}

\cvline{[\thecount]}{Jialu Fan, Rui liu, \textbf{Yi Jiang}, Tianyou Chai. Operation control system and method of single tank water tank based on wireless communication. China: 201510776737.7. (Date of authorization: 2017/12/29)}\addtocounter{count}{1}
\cvline{[\thecount]}{Jialu Fan, \textbf{Yi Jiang}, Tianyou Chai. Flotation industrial process operational control system and method under a class of double network environments. China: 2014101756.32. (Date of authorization: 2016/03/04)}\addtocounter{count}{1}

\section{Invited Talk}\setcounter{count}{1}

\cvline{[\thecount]}{Data driven optimal tracking control method and its application in network control system. ``I have an appointment with an excellent doctor'' excellent doctor of China automation society, December 27-28, 2019, Harbin, China.}\addtocounter{count}{1}
\cvline{[\thecount]}{Optimal Output Regulation of Linear Discrete-Time Systems with Unknown Dynamics Using Off-Policy Reinforcement Learning. The 3rd International Symposium on Autonomous Systems, ISAS 2019, May 29-31, 2019, Shanghai, China.}\addtocounter{count}{1}

\section{Services}
%

\cvline{}{\textbf{Journal Service:}}\setcounter{count}{1}
\cvline{[\thecount]}{Associate Editor of Advanced Control for Applications: Engineering and Industrial Systems (2020-present)}\addtocounter{count}{1}

\cvline{}{\textbf{Journal Reviewer:}}\setcounter{count}{1}
\cvline{[\thecount]}{IEEE Transactions on Automatic Control}\addtocounter{count}{1}
\cvline{[\thecount]}{Automatica}\addtocounter{count}{1}
\cvline{[\thecount]}{IEEE Transactions on Neural Networks and Learning Systems}\addtocounter{count}{1}
\cvline{[\thecount]}{IEEE Transactions on Systems, Man and Cybernetics: Systems}\addtocounter{count}{1}
\cvline{[\thecount]}{International Journal of Robust and Nonlinear Control}\addtocounter{count}{1}
\cvline{[\thecount]}{Industrial \& Engineering Chemistry Research}\addtocounter{count}{1}
\cvline{[\thecount]}{Neurocomputing}\addtocounter{count}{1}
\cvline{[\thecount]}{Optimal Control, Applications and Methods}\addtocounter{count}{1}
\cvline{[\thecount]}{Wireless Communications and Mobile Computing}\addtocounter{count}{1}
\cvline{[\thecount]}{Journal of Control Theory and Applications}\addtocounter{count}{1}
\cvline{[\thecount]}{Journal of Applied Sciences}\addtocounter{count}{1}
\cvline{[\thecount]}{Control Engineering of China}\addtocounter{count}{1}
%

\cvline{}{\textbf{Conference Service:}}\setcounter{count}{1}
\cvline{[\thecount]}{Committee participation of 2018 IEEE International Conference on Information and Automation (ICIA)}\addtocounter{count}{1}
\cvline{[\thecount]}{2017 Chinese Process Control Conference (CPCC) Session Associate Chair}\addtocounter{count}{1}

\cvline{}{\textbf{Conference Reviewer:}}\setcounter{count}{1}
\cvline{[\thecount]}{IEEE Conference on Decision and Control (CDC)}\addtocounter{count}{1}
\cvline{[\thecount]}{American Control Conference (ACC)}\addtocounter{count}{1}
\cvline{[\thecount]}{Chinese Control  Conference (CCC)}\addtocounter{count}{1}
\cvline{[\thecount]}{World Congress on Intelligent Control and Automation (WCICA)}\addtocounter{count}{1}
\cvline{[\thecount]}{Chinese Control and Decision Conference (CCDC)}\addtocounter{count}{1}
\cvline{[\thecount]}{Data Driven Control and Learning Systems Conference (DDCLS)}\addtocounter{count}{1}
\cvline{[\thecount]}{IEEE International Conference on Information and Automation (ICIA)}\addtocounter{count}{1}

%

%
\cvline{}{\textbf{Membership:}}\setcounter{count}{1}
\cvline{[\thecount]}{IEEE Student Member, 2014-2020}\addtocounter{count}{1}
\cvline{[\thecount]}{IEEE Member, 2020-present}\addtocounter{count}{1}

\section{Academic Conferences Experiences}

\cventry{2019/7}{The 1st International Conference on Industrial Artificial Intelligence}{}{July 23 - 25, 2017}{Shenyang, Liaoning, China}{}{}
\cventry{2019/5}{The 3rd International Symposium on Autonomous Systems}{}{May 29-31}{Shanghai, China}{}{}
\cventry{2017/7}{The 28th Chinese Process Control Conference}{}{July 29 - August 1, 2017}{Chongqing, China}{}{}
\cventry{2016/11}{The 4th Chinese Automation Academic annual Congress of the Academy of youth}{}{November 11 - 13, 2016}{Wuhan, China}{}{}
\cventry{2015/11}{The 4th Chinese Automation Congress}{}{November 27 - 29, 2015}{Wuhan, China}{}{}
\cventry{2015/8}{The 26th Chinese Process Control Conference}{}{July 31 - August 3, 2015}{Nanchang, China}{}{}
\cventry{2015/7}{The 2015 American Control Conference}{}{July 1-3, 2015}{Chicago, America}{}
\cventry{2014/8}{The 25th Chinese Process Control Conference}{}{August 9-11, 2014}{Dalian, China}{}{}
\cventry{2014/7}{The 1st International Conference on Mechatronics and Control}{}{July 3-5, 2014}{Jinzhou, China}{}
\cventry{2014/6}{The 11th World Congress on Intelligent Control and Automation}{}{June 29 - July 4, 2014}{Shenyang, China}{}

\section{Scholarships}

\cventry{2018/10}{National Scholarships}{}{}{Ministry of Education, China}{}{}
\cventry{2018/7}{Excellent Doctoral Scholarship of Northeastern University}{}{}{Northeastern University}{}{}
\cventry{2018/5}{Excellent Doctoral Scholarship of Zhang Siying Education Fund}{}{}{Zhang Siying Education Fund}{}{}
\cventry{2015/10}{National Scholarships}{}{}{Ministry of Education, China}{}{}
\cventry{2015/9}{First Class Award Scholarship of the Graduate School}{}{}{Northeastern University}{}{}
\cventry{2014/9}{First Class Award Scholarship of the Graduate School}{}{}{Northeastern University}{}{}
\cventry{2013-2014}{Second Class Award Scholarship of the First Term}{}{}{Northeastern University}{}{}
\cventry{2012-2013}{Second Class Award Scholarship of the Second Term}{}{}{Northeastern University}{}{}
\cventry{2012-2013}{Second Class Award Scholarship of the First Term}{}{}{Northeastern University}{}{}
\cventry{2011-2012}{Third Class Award Scholarship of the Second Term}{}{}{Northeastern University}{}{}
\cventry{2011-2012}{Second Class Award Scholarship of the First Term}{}{}{Northeastern University}{}{}
\cventry{2010-2011}{Second Class Award Scholarship of the Second Term}{}{}{Northeastern University}{}{}

\section{Honors}

\cventry{2019}{Excellent Communist Party Members of Information Science and Engineering College}{}{}{Northeastern University}{}{}
\cventry{2019}{"May4th Youth Medal" Ten Excellent Graduate Student of Northeastern University}{}{}{Northeastern University}{}{}
\cventry{2018}{Excellent Graduate Students in Shenyang}{}{}{Department of Education, Shenyang}{}{}
\cventry{2018}{Excellent Graduate Student of Northeastern University}{}{}{Northeastern University}{}{}
\cventry{2017/12}{Outstanding Scholar Award of State Key Lab of Synthetic Automation of Process Industries}{}{}{State Key Lab of Synthetic Automation of Process Industries, Northeastern University}{}{}
\cventry{2016/12}{Outstanding Scholar Award of State Key Lab of Synthetic Automation of Process Industries}{}{}{State Key Lab of Synthetic Automation of Process Industries, Northeastern University}{}{}
\cventry{2017/9}{Outstanding Graduate Thesis of Chinese Society of Metallurgical education}{}{}{Chinese Society of Metallurgical education, Ministry of Education, China}{}{}
\cventry{2016/9}{Outstanding Graduate Thesis of 2016 Degree}{}{}{Liaoning Provincial}{}{}
\cventry{2016/9}{Outstanding Graduate Thesis of 2016 Degree}{}{}{Northeastern University}{}{}
\cventry{2016/7}{Japan ``Sakula Science'' Youth Project}{}{}{Japanese Government}{}{}
\cventry{2015}{Excellent Graduate Students in Shenyang}{}{}{Department of Education, Shenyang}{}{}
\cventry{2015}{Excellent Graduate Student of Northeastern University}{}{}{Northeastern University}{}{}
\cventry{2014/9}{Outstanding Undergraduate Thesis of 2014 Degree}{}{}{Northeastern University}{}{}
\cventry{2014}{Innovation Credit Honor (12 credits)}{}{}{Northeastern University}{}{}
\cventry{2012-2013}{Excellent League Member of Northeastern University}{}{}{Northeastern University}{}{}
\cventry{2012-2013}{Excellent Personal in Science and Technology Innovation of Northeastern University}{}{}{Northeastern University}{}{}
\cventry{2011-2012}{Excellent League Member of Northeastern University}{}{}{Northeastern University}{}{}

\section{Awards}

\cventry{2018/9}{Best Paper Award in 2018 International Conference on Advance Mechatronic Systems (ICAMechS)}{}{}{}{}{}
\cventry{2018/7}{Excellent Student Paper Award in 29th Chinese Process Control Conference (CPCC)}{}{}{}{}{}
\cventry{2013/12}{The Second Award of 2013 National Undergraduate Electronic Design Contest}{}{}{Organization Committee of National Undergraduate Electronic Design Contest, Ministry of Education}{}{}
\cventry{2013/12}{The First Award of 2013 ``TI'' Cup Liaoning Provincial Undergraduate Electronic Design Contest}{}{}{Liaoning Provincial Education Department}{}{}
\cventry{2013/7}{The Second Award of the eighth ``Freescale'' Cup National Undergraduate Smart Car Contest in Northeast Division}{}{}{Ministry of Education}{}{}
\cventry{2013/2}{The Meritorious Winner (The first award) of 2013 American Mathematical Contest in Modeling}{}{}{COMAP: Consortium for Mathematics and Its Applications}{}{}
\cventry{2012/9}{The Third Award of Liaoning Provincial National Undergraduate Mathematical Contest in Modeling}{}{}{Liaoning Provincial Mathematics Committee}{}{}
\cventry{2012/8}{The Second Award of 2012 ``TI'' Cup Liaoning Provincial Undergraduate Electronic Design Contest}{}{}{Liaoning Provincial Education Department}{}{}
\cventry{2012/6}{The Second Award of International Undergraduate Mathematical Contest in Modeling in Chinese Division}{}{}{Organization Committee of  International Undergraduate Mathematical Contest in Modeling}{}{}
\cventry{2011/12}{The First Award of the Third Liaoning Provincial National Undergraduate Mathematical Contest}{}{}{Liaoning Provincial Mathematics Committee}{}{}
\cventry{2011/6}{The Second Award of Northeastern University Mechanical Drawing Contest}{}{}{Northeastern University}{}{}

\section{Skills}

\cvline{Programing language}{C, C++, C\#, JAVA, C51, Embedded C for Freescale Kinetis, Assembly Language, MATLAB, VHDL, \LaTeX{}, OpenCV}

\cvline{Software}{Multisim, Step 7, WinCC, Altium Designer 9, Protel 99 SE, CAXA, Solidworks, Microsoft Office, SPSS, Keil, IAR Embedded Workbench, Code Composer Studio, CodeWarrior, Visual Studio}


\nocite{*}
\bibliographystyle{plain}
\bibliography{jdoe_publications}
\end{CJK*}
\end{document}




